Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-30 Scripts/Initial_Analysis.Rmd
Updated figures S

lat_am_map <- ggplot(toe_map_data) +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation, 
                color = participation),
            # color =  "white",
            size = 0.1
    ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", 
            # color =  "white",
            size = 0.1) +
    # geom_sf(data = grey_eez, aes(), fill = "white", color =  "grey50",size = 0.1) +
    geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
  coord_sf(xlim = c(-9000000,-5000000),ylim = c(1000000, 4000000)) + 
  facet_wrap(~tresh) +
  scale_colour_viridis("",
                         limits = c(2000,2100),
                         breaks = seq(2000,2100,25),
                         # labels = c("","","","",""),
                         direction = 1
    ) +
    scale_fill_viridis("",
                         limits = c(2000,2100),
                         breaks = seq(2000,2100,25),
                         # labels = c("","","","",""),
                         direction = 1
    ) +
    my_ggtheme_m(map_type = "regional",leg_pos = "")

ggsave("lat_am_map.png",
       lat_am_map,
       width = 8,
       height = 6)

@@

spi_map <-  ggplot(spi_toe_map_data) +
  geom_sf(
    aes(
      fill = reverse #original map
      # fill = value
    ),
    color =  "white",
    size = 0.1
  ) +
  # Inlcude the participation of species
  geom_sf(data = spi_map_part,
          # aes(fill = participation+2000), #original map
          aes(fill = participation, 
              color = participation),
          # color =  "white",
          size = 1
  ) +
  # grey maps
  geom_sf(data = spi_no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
  geom_sf(data = spi_no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
  coord_sf(xlim = c(9500000,1000000),ylim = c(-3500000, 1900000)) + 
  facet_wrap(~tresh) +
  scale_colour_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       # labels = c("","","","",""),
                       direction = 1
  ) +
  scale_fill_viridis("",
                     limits = c(2000,2100),
                     breaks = seq(2000,2100,25),
                     # labels = c("","","","",""),
                     direction = 1
  ) +
  scale_x_continuous(limits = c(-120,180),
                     breaks = c(-120,180)
                     # labels =c("a","b")
  ) + 
  my_ggtheme_m(map_type = "regional",leg_pos = "bottom") +
  theme(legend.key.width = unit(3, "line"))

ggsave(".Figures/spi_map_bf.png",
       spi_map,
       width = 8,
       height = 6)
```

@@

```{r ssr_map_data, eval = T, echo = T}
# A function that makes a dateframe per connection (we will use these connections to plot each lines)
data_for_connection=function( dep_lon, dep_lat, arr_lon, arr_lat, group){
  inter <- gcIntermediate(c(dep_lon, dep_lat), c(arr_lon, arr_lat), n=50, addStartEnd=TRUE, breakAtDateLine=F)             
  inter=data.frame(inter)
  inter$group=NA
  diff_of_lon=abs(dep_lon) + abs(arr_lon)
  if(diff_of_lon > 180){
    inter$group[ which(inter$lon>=0)]=paste(group, "A",sep="")
    inter$group[ which(inter$lon<0)]=paste(group, "B",sep="")
  }else{
    inter$group=group
  }
  return(inter)
}

@@

```{r}
# SELECT A TIME STEP
# time_toplot <- "per_mid"
time_toplot <- "per_early"
```

@@

lat_am_map <- ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,
          col = "white") +
  # geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
  geom_path(data = subset(arrows_data, percentage >= 0),
            aes(X, Y,
                group = group,
                col = percentage
            ),
            size = 1,
            arrow = arrow(length = unit(0.03, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-9000000,-5000000),ylim = c(1000000, 4000000)) + 
  labs(x = "", y = "") +
  # scale_x_continuous(breaks = seq(-100,60,10)) +
  # scale_y_continuous(breaks = seq(10,30,10)) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(
    panel.background = element_rect(fill = "white", color = "white"),
    panel.grid.major =  element_line(color = "white")
  ) +
  scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(Lat_am_data$percentage)),
                        breaks = seq(0,max(Lat_am_data$percentage),10)
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                       colours = pal,
                       limits = c(0,max(Lat_am_data$percentage)),
                       breaks = seq(0,max(Lat_am_data$percentage),10)
  ) + guides(
    color=guide_colorbar(title.position="top", 
                         title.hjust =0.5)
  ) +
  theme(legend.key.width = unit(4,"line"))

ggsave(filename = "lat_am_mid.png",
       lat_am_map,
       width = 6,
       height = 6)

@@

EU_map <- ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,
          col = "white") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
  geom_path(data = subset(arrows_data, percentage >= 0),
            aes(X, Y,
                group = group,
                col = percentage
            ),
            size = 1,
            arrow = arrow(length = unit(0.03, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-1300000,2000000),ylim = c(5500000, 7500000))  +
  labs(x = "", y = "") +
  scale_x_continuous(breaks = seq(-100,60,10)) +
  scale_y_continuous(breaks = seq(10,30,10)) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(
    panel.background = element_rect(fill = "white", color = "white"),
    panel.grid.major =  element_line(color = "white")
  ) +
  scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(EU_data$percentage)),
                        breaks = seq(0,max(EU_data$percentage),10)
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                       colours = pal,
                       limits = c(0,max(EU_data$percentage)),
                       breaks = seq(0,max(EU_data$percentage),10)
  ) + guides(
    color=guide_colorbar(title.position="top",
                         title.hjust =0.5)
  ) +
  theme(legend.key.width = unit(4,"line"))

ggsave(filename = "EU_early.png",
       EU_map,
       width = 6,
       height = 6)

>>>>

lat_am_map <- ggplot(toe_map_data) +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation, 
                color = participation),
            # color =  "white",
            size = 0.1
    ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", 
            # color =  "white",
            size = 0.1) +
    # geom_sf(data = grey_eez, aes(), fill = "white", color =  "grey50",size = 0.1) +
    geom_sf(data = no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
  coord_sf(xlim = c(-9000000,-5000000),ylim = c(1000000, 4000000)) + 
  facet_wrap(~tresh, ncol = 1) +
  scale_colour_viridis("",
                         limits = c(2000,2100),
                         breaks = seq(2000,2100,25),
                         # labels = c("","","","",""),
                         direction = 1
    ) +
    scale_fill_viridis("",
                         limits = c(2000,2100),
                         breaks = seq(2000,2100,25),
                         # labels = c("","","","",""),
                         direction = 1
    ) +
    my_ggtheme_m(map_type = "regional",leg_pos = "")

ggsave("Figures/lat_am_map.png",
       lat_am_map,
       width = 6,
       height = 8)

@@

spi_map <-  ggplot(spi_toe_map_data) +
  geom_sf(
    aes(
      fill = reverse #original map
      # fill = value
    ),
    color =  "white",
    size = 0.1
  ) +
  # Inlcude the participation of species
  geom_sf(data = spi_map_part,
          # aes(fill = participation+2000), #original map
          aes(fill = participation, 
              color = participation),
          # color =  "white",
          size = 1
  ) +
  # grey maps
  geom_sf(data = spi_no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
  geom_sf(data = spi_no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
  coord_sf(xlim = c(9500000,1000000),ylim = c(-3500000, 1900000)) + 
  facet_wrap(~tresh, ncol = 1) +
  scale_colour_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       # labels = c("","","","",""),
                       direction = 1
  ) +
  scale_fill_viridis("",
                     limits = c(2000,2100),
                     breaks = seq(2000,2100,25),
                     # labels = c("","","","",""),
                     direction = 1
  ) +
  scale_x_continuous(limits = c(-120,180),
                     breaks = c(-120,180)
                     # labels =c("a","b")
  ) + 
  my_ggtheme_m(map_type = "regional",leg_pos = "bottom") +
  theme(legend.key.width = unit(3, "line"))

ggsave("Figures/spi_map_bf.png",
       spi_map,
       width = 6,
       height = 8)
```

@@

```{r ssr_map_data, eval = T, echo = T}
# A function that makes a dataframe per connection (we will use these connections to plot each lines)
data_for_connection=function( dep_lon, dep_lat, arr_lon, arr_lat, group){
  inter <- gcIntermediate(c(dep_lon, dep_lat), c(arr_lon, arr_lat), n=50, addStartEnd=TRUE, breakAtDateLine=F)             
  inter=data.frame(inter)
  inter$group=NA
  diff_of_lon=abs(dep_lon) + abs(arr_lon)
  if(diff_of_lon > 180){
    inter$group[ which(inter$lon>=0)]=paste(group, "A",sep="")
    inter$group[ which(inter$lon<0)]=paste(group, "B",sep="")
  }else{
    inter$group=group
  }
  return(inter)
}

@@

```{r}
# SELECT A TIME STEP
time_toplot <- "per_mid"
# time_toplot <- "per_early"
```

@@

lat_am_map <- ggplot() +
  # PLot EEZs
  geom_sf(data = subset(World_eez_sf,
                        !str_detect(eez_name,"Pacific") &
                        !str_detect(eez_name,"El Salvador") &
                        !eez_name %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil")
  ), size = 0.1, fill = "white", col = "gray30") +
  # Plot Land information
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,
          col = "white") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0 & 
                          !str_detect(source,"Pacific") & 
                        !source %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil","El Salvador") &
                        !str_detect(objective,"Pacific") &
                        !objective %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil","El Salvador")
                        ), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = subset(point_data,
                        !str_detect(source,"Pacific") & 
                        !source %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil","El Salvador") &
                        !str_detect(target,"Pacific") &
                        !target %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil","El Salvador")
                        ),
          aes(), color = "grey90") +
  geom_path(data = subset(arrows_data, percentage >= 0 &
                            !str_detect(objective,"Pacific") &
                        !objective %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil","El Salvador")
                        ),
            aes(X, Y,
                group = group,
                col = percentage
            ),
            size = 1,
            arrow = arrow(length = unit(0.03, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-9000000,-5000000),ylim = c(1000000, 4000000)) + 
  labs(x = "", y = "") +
  # scale_x_continuous(breaks = seq(-100,60,10)) +
  # scale_y_continuous(breaks = seq(10,30,10)) +
  my_ggtheme_m(map_type = "NA",leg_pos = "bottom") +
  theme(
    panel.background = element_rect(fill = "white", color = "white"),
    panel.grid.major =  element_line(color = "white")
  ) +
  scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,50),
                        breaks = seq(0,50,10)
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                       colours = pal,
                       limits = c(0,50),
                        breaks = seq(0,50,10)
  ) + guides(
    color=guide_colorbar(title.position="top", 
                         title.hjust =0.5)
  ) +
  theme(legend.key.width = unit(4,"line"))

name <- paste0("Figures/lat_am_",time_toplot,".png")

ggsave(filename = name,
       lat_am_map,
       width = 6,
       height = 6)

@@

# Name to save
name_eu <- paste0("Figures/EU_",time_toplot,".png")

# PLot EU map
EU_map <- ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = avrg_spp_per),
          size = 0.1,
          col = "white") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
  geom_path(data = subset(arrows_data, percentage >= 0),
            aes(X, Y,
                group = group,
                col = percentage
            ),
            size = 1,
            arrow = arrow(length = unit(0.03, "npc"),
                          ends = "first"),
            show.legend = NA) +
  coord_sf(xlim = c(-1300000,2000000),ylim = c(5500000, 7500000))  +
  labs(x = "", y = "") +
  scale_x_continuous(breaks = seq(-100,60,10)) +
  # scale_y_continuous(breaks = seq(10,30,10)) +
  my_ggtheme_m(map_type = "NA",leg_pos = "bottom") +
  theme(
    panel.background = element_rect(fill = "white", color = "white"),
    panel.grid.major =  element_line(color = "white")
  ) +
  scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,50),
                        breaks = seq(0,50,10)
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                       colours = pal,
                       limits = c(0,50),
                        breaks = seq(0,50,10)
  ) + guides(
    color=guide_colorbar(title.position="top",
                         title.hjust =0.5)
  ) +
  theme(legend.key.width = unit(4,"line"))

# Save map
ggsave(filename = name_eu,
       EU_map,
       width = 6,
       height = 6)
